\mytitle

### 2021-12-06 paper.tex
improve affiliation
refine text

\title{\mytitle}
\author{\myauthor}
\affil{Fachbereich Energie und Biotechnologie, Hochschule Flensburg, Kanzleistraße 91--93, 24943 Flensburg, Germany}
\date{\today}

@@

\section{Comparison of algorithms}

As an example we consider the function $\log(1+x)$, which has the
following Taylor expansion around $x=0$ for $-1 < x \leq 1$:
%
\begin{align}
  \log(1+x) \approx x - \frac{x^2}{2} + \frac{x^3}{3} - \frac{x^4}{4} + \frac{x^5}{5} - \frac{x^6}{6} + \frac{x^7}{7},
  \label{eq:taylor}
\end{align}
%
where terms of $O(x^8)$ have been omitted.
In C this function could be implemented as follows:
%
\begin{lstlisting}[language=C]
double log1p_naive(double x) {
   return x - x*x/2 + x*x*x/3 - x*x*x*x/4
      + x*x*x*x*x/5 - x*x*x*x*x*x/6
      + x*x*x*x*x*x*x/7;
}
\end{lstlisting}
%
This naive implementation requires 26 floating-point multiplications
and 6 floating-point additions.\footnote{Modern compilers usually
  rewrite expensive floating-point divisions by a constant, such as
  $x/2$, as less expensive floating-point multiplication by a
  constant, for example as $0.5x$.}

>>>>

\title{\mytitle}
\author{\myauthor}
\affil{Fachbereich Energie und Biotechnologie, Hochschule Flensburg,\\ Kanzleistra{\ss}e 91--93, 24943 Flensburg, Germany}
\date{\today}

@@

\section{Performance comparison of different implementation strategies}

As a toy example we consider the function $\log(1+x)$, which has the
Taylor expansion
%
\begin{align}
  \log(1+x) \approx x - \frac{x^2}{2} + \frac{x^3}{3} - \frac{x^4}{4} + \frac{x^5}{5} - \frac{x^6}{6} + \frac{x^7}{7}
  \label{eq:taylor}
\end{align}
%
around $x=0$ for $x\in(-1,1]$, where terms of $O(x^8)$ and beyond have
been omitted.  In the following we will briefly study various possible
implementations of this function and compare the performance of the
different implementations.  For brevity we will restrict ourselves to
$x\in(-1,1]$.  In C the function in Eq.~\eqref{eq:taylor} could be
implemented very naively as follows:
%
\begin{lstlisting}[language=C]
double log1p_naive(double x) {
   return x - x*x/2 + x*x*x/3 - x*x*x*x/4
      + x*x*x*x*x/5 - x*x*x*x*x*x/6
      + x*x*x*x*x*x*x/7;
}
\end{lstlisting}
%
This naive implementation requires 26 floating-point multiplications
and 6 floating-point additions.\footnote{Modern compilers usually
  rewrite expensive floating-point divisions by a constant, such as
  $x/2$, as less expensive floating-point multiplication by a
  constant, for example as $0.5x$.  In the following we will therefore
  count a division of a variable by a constant as a floating-point
  multiplication.}
